---
title: "Implicit Learning Experiment 0 Analysis"
output: html_notebook
---

```{r}
library(rjson)
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(lmerTest)
```

# Data loading
```{r}
num_subjects = 42
data_dir = "../anonymized_data/ex0"
```

```{r, message=F, warning=F}
auxiliary_data = list()
main_data = data.frame()
question_data = data.frame()
for (i in 1:num_subjects) {
  if (!all(file.exists(c(
    sprintf("%s/%s/%i.json", data_dir,"aux",i),
    sprintf("%s/%s/%i.json", data_dir,"s0",i),
    sprintf("%s/%s/%i.json", data_dir,"s1",i),
    sprintf("%s/%s/%i.json", data_dir,"s2",i)
  )))) {
    print(sprintf("Skipping %i -- missing file", i))
    next
  }
  aux_d_list = fromJSON(file=sprintf("%s/%s/%i.json", data_dir,"aux",i))
  aux_d_frame = data.frame(aux_d_list[c("fractal_dihedral", "isomorphic")])
  aux_d_frame$subject_id = i
  aux_d_frame$this_fractal_assignment = list(aux_d_list$this_fractal_assignment)
  aux_d_frame$this_room_assignment = list(aux_d_list$this_room_assignment)
  aux_d_frame$this_mutagen_assignment = list(aux_d_list$this_mutagen_assignment)
  aux_d_frame$this_door_color_assignment = list(aux_d_list$this_door_color_assignment)
  aux_d_frame$this_door_generator_assignment = list(aux_d_list$this_door_generator_assignment)
  auxiliary_data = rbind(auxiliary_data, aux_d_frame)
  
  for (s in 0:2) {
    main_d_list = fromJSON(file=sprintf("%s/s%i/%i.json", data_dir,s,i))
    main_d_frame = data.frame()
    question_d_frame = data.frame()
    for (trial_i in 1:length(main_d_list)) {
      this_trial = main_d_list[[trial_i]]
      
      if (this_trial$trial_type == "two-door-navigation" | this_trial$trial_type == "fractal-mutation") {
        # data trial
        this_trial$location_rts = fromJSON(this_trial$location_rts)
        this_trial$action_history = fromJSON(this_trial$action_history)
        this_trial$location_history = fromJSON(this_trial$location_history)[1:length(this_trial$action_history)] # chop off known last location
        
        this_trial_d = data.frame(this_trial[c("trial_type", "group", "start", "goal", "action_noise", "trial_index", "time_elapsed", "location_history", "action_history", "location_rts")])
        this_trial_d$session = s
#        if (this_trial$trial_type == "two-door-navigation") {
#          this_trial_d$object_history = list(fromJSON(this_trial$door_history))
#        } else {
#          this_trial_d$object_history = list(fromJSON(this_trial$mutagen_history))
#        }
        main_d_frame = bind_rows(main_d_frame, this_trial_d)
      } else if (grepl("survey",this_trial$trial_type)) {
        # debrief or demographics
        parsed_responses = fromJSON(this_trial$responses)
        for (name in names(parsed_responses)) {
          this_Q_d = data.frame(this_trial[c("trial_type", "rt", "trial_index", "time_elapsed")])
          this_Q_d$session = s
          this_Q_d$name = name
          this_Q_d$response = parsed_responses[[name]]
          question_d_frame = bind_rows(question_d_frame, this_Q_d)
        }
      } else {
        # instructions or other
        next
      }
    }
    main_d_frame$subject_id = i
    main_data = bind_rows(main_data, main_d_frame)
    if (nrow(question_d_frame) > 0) {
      question_d_frame$subject_id = i
      question_data = bind_rows(question_data, question_d_frame)
    }
  }
}

auxiliary_data = data.frame(auxiliary_data)
main_data = data.frame(main_data)
question_data = data.frame(question_data)
```
# fake data (for development purposes only)
```{r}
# auxiliary_data = bind_rows(auxiliary_data, auxiliary_data, auxiliary_data, auxiliary_data)
# auxiliary_data$subject_id = c(2, 3, 4, 5)
# auxiliary_data$fractal_dihedral = c(F, T, F, T)
# auxiliary_data$isomorphic = c(F, F, T, T)
# 
# mdlen = nrow(main_data)
# main_data = bind_rows(main_data, main_data, main_data, main_data)
# main_data$subject_id = rep(c(2, 3, 4, 5), each=mdlen)
# 
# 
# qdlen = nrow(question_data)
# question_data = bind_rows(question_data, question_data, question_data, question_data)
# question_data$subject_id = rep(c(2, 3, 4, 5), each=qdlen)
```


# data manipulation
Easy get of condition variables
```{r}
main_data = inner_join(main_data, 
                       auxiliary_data %>%
                         select(fractal_dihedral, isomorphic, subject_id))
```

Some renaming for convenience/clarity
```{r}
main_data = main_data %>%
  rename(location=location_history, action=action_history) %>%
  mutate(group = ifelse(grepl("dihedral", group), "dihedral", "dicyclic"),
         trial_type = ifelse(grepl("fractal", trial_type), "fractal", "door"))
```

Load correct action info
```{r}
d6_opt_tab = read.csv('group_utils/d6_table.csv', header=F)
d6_opt_tab[d6_opt_tab == -1] = NA
dc12_opt_tab = read.csv('group_utils/dc12_table.csv', header=F)
dc12_opt_tab[dc12_opt_tab == -1] = NA

d6_optimal_action = function(state, goal) {
  return(d6_opt_tab[state+1, goal+1])
}
d6_optimal_action = Vectorize(d6_optimal_action)

dc12_optimal_action = function(state, goal) {
  return(dc12_opt_tab[state+1, goal+1])
}
dc12_optimal_action = Vectorize(dc12_optimal_action)
```

Label actions as correct or incorrect
```{r}
main_data = main_data %>%
  mutate(correct_action = ifelse(group=="dihedral",
                                 d6_optimal_action(location, goal),
                                 dc12_optimal_action(location, goal)),
         action_correct = action == correct_action)
```

# question data manipulation

```{r}
question_data = question_data %>%
  mutate(question = ifelse(session < 2 | trial_index == 86,
                           "comments",
                    ifelse(trial_index == 75,
                           "door_hyp_guess",
                    ifelse(trial_index == 76,
                           "fractal_hyp_guess",
                    ifelse(trial_index == 77,
                           "similarity_likert",
                    ifelse(trial_index == 78,
                           "similarity_descr",
                    ifelse(trial_index == 79,
                           "correspondence_suspect",
                    ifelse(trial_index == 80,
                           "when_noticed",
                    ifelse(trial_index == 81,
                           "correspondence_descr",
                    ifelse(trial_index == 82,
                           "one_task_helpful_for_other",
                    ifelse(trial_index == 83,
                           "which_condition",
                    ifelse(trial_index == 84 & name == "Q0",
                           "correspondence_identify",
                    ifelse(trial_index == 84 & name == "Q1",
                           "correspondence_identify_confidence",
                    ifelse(trial_index == 85 & name == "Q0",
                           "age",
                    ifelse(trial_index == 85 & name == "Q1",
                           "education",
                    ifelse(trial_index == 85 & name == "Q2",
                           "gender",
                    ifelse(trial_index == 85 & name == "Q3",
                           "race",
                           NA)))))))))))))))))

any(is.na(question_data$question))
```

hacky way of doing exactly the comparison I want to do (vector-wise comparison of vectors whose elements are lists).
```{r}
compare_lists_of_lists = function(l1, l2) {
  res = c()
  for (i in 1:length(l1)) {
    if (identical(l1[[i]], l2[[i]])) {
      this_res = T
    }
    else {
      this_res = F
    }
    res = c(res, this_res)
  }
  return(res)
}

compare_lol_to_list = function(lol, l) {
  res = c()
  for (i in 1:length(lol)) {
    if (identical(lol[[i]], l)) {
      this_res = T
    }
    else {
      this_res = F
    }
    res = c(res, this_res)
  }
  return(res)
}
```

```{r}
question_data = inner_join(question_data,
                           auxiliary_data %>%
                             select(fractal_dihedral,
                                    isomorphic,
                                    this_door_color_assignment,
                                    this_door_generator_assignment,
                                    this_mutagen_assignment,
                                    subject_id)) %>%
  mutate(correct_correspondence = ifelse(!isomorphic, NA, ifelse((compare_lol_to_list(this_door_color_assignment, list(c("white", "black"))) & compare_lists_of_lists(this_door_generator_assignment, this_mutagen_assignment)) | (compare_lol_to_list(this_door_color_assignment, list(c("black", "white"))) & !compare_lists_of_lists(this_door_generator_assignment, this_mutagen_assignment)), "white door = acid, black door = ray", "black door = acid, white door = ray")),
         correspondence_correct = ifelse(question != "correspondence_identify", NA, response == correct_correspondence))
```

```{r}
question_data = question_data %>%
  mutate(subject_id = factor(subject_id))
```

# demographics

```{r}
demographic_data = question_data %>%
  filter(question %in% c("race", "gender", "age", "education")) %>%
  select(subject_id, question, response) %>%
  spread(question, response)  %>%
  mutate(education_high = grepl("PhD|Master|Bachelor", education))
  
```

factoring
```{r}
main_data = main_data %>% 
  mutate(trial_type = factor(trial_type),
         group = factor(group),
         subject_id = factor(subject_id))
```

```{r}
main_data = inner_join(main_data, demographic_data) 
```


# More main data + collapsed data

Centering as appropriate
```{r}
main_data = main_data %>%
  mutate(session_c = session-1, #scale(session, center=T, scale=F), # center session variable
         trial_index_by_type = ifelse(trial_type == "fractal", trial_index - 37, trial_index), # align indices for door and fractal trials
         trial_index_by_type_z = scale(trial_index_by_type, center=T, scale=T))
```



```{r}
collapsed_main_data = main_data %>%
  group_by(subject_id, isomorphic, fractal_dihedral, group, trial_type, session) %>%
  summarize(pct_correct = sum(action_correct, na.rm=T)/sum(!is.na(action_correct)))
```

```{r}
fully_summarized_data = collapsed_main_data %>%
  group_by(isomorphic, group, session) %>%
  summarize(mean_pct_correct = mean(pct_correct), sd_pct_correct = sd(pct_correct)) %>%
  mutate(c95_lower = mean_pct_correct - 1.96*sd_pct_correct/sqrt(n()),
         c95_upper = mean_pct_correct + 1.96*sd_pct_correct/sqrt(n()))
```

# Most basic analyses
```{r}
theme_set(theme_bw() +
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
```



```{r}
ggplot(data=collapsed_main_data, aes(x=isomorphic, y=pct_correct, fill=group)) +
  geom_violin()
```

```{r}
ggplot(data=collapsed_main_data, aes(x=session, y=pct_correct, color=isomorphic, group=interaction(subject_id, isomorphic, group, trial_type))) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept=0.5, alpha=0.75, linetype=2) +
#  ylim(0,1) +
  facet_wrap(~ group)
```

```{r}
ggsave("figures/ex0/curve_plot.png", width=7,height=5)
```


```{r}
ggplot(data=fully_summarized_data, aes(x=factor(session), y=mean_pct_correct, fill=isomorphic)) +
  geom_bar(stat="identity",position="dodge") +
  geom_errorbar(aes(ymin=c95_lower, ymax = c95_upper), position=position_dodge(width=1), width=0.5) +
  geom_hline(yintercept=0.5, alpha=0.75, linetype=2) +
  ylim(0,1) +
  facet_wrap(~ group)
```

```{r}
ggsave("figures/ex0/basic_plot.png", width=7,height=5)
```

Appears to be absolutely no learning in the dicyclic condition (although increasing errorbars in the isomorphic condition reflect the fact that at least one subject may have learned...)

Just looking at condition and extremely important controls and random effects
```{r}
basic_non_time_dependent_model = glmer(action_correct ~ isomorphic + group * correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2) + (1  | subject_id), family=binomial, data=main_data)
summary(basic_non_time_dependent_model)
```

Time dependent:
```{r}
basic_time_dependent_model = glmer(action_correct ~ isomorphic + session_c + I(session_c^2) + group * correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 +session_c | subject_id), family=binomial, data=main_data)
summary(basic_time_dependent_model)
```


```{r}
time_dependent_interaction_model = glmer(action_correct ~ isomorphic * (session_c + I(session_c^2))  + group *  correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c  | subject_id), family=binomial, data=main_data)
summary(time_dependent_interaction_model)
```



```{r}
rt_time_dependent_interaction_model = lmer(location_rts/1000~ isomorphic * (session_c + I(session_c^2)) + group + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 | subject_id), data=main_data)
summary(rt_time_dependent_interaction_model)
```

```{r}
num_steps_per_trial_data = main_data %>%
  group_by(subject_id, isomorphic, session_c, group, trial_type, trial_index_by_type_z) %>%
  summarize(num_steps_needed=n())
```

```{r}
ns_time_dependent_interaction_model = lmer(num_steps_needed~ isomorphic * (session_c + I(session_c^2)) + group + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 | subject_id), data=num_steps_per_trial_data)
summary(ns_time_dependent_interaction_model)
```



# Joining data
```{r}
s2_joined_question_data = inner_join(question_data,
                                     collapsed_main_data %>%
                                       group_by(subject_id, session, isomorphic, group) %>%
                                       summarize(pct_correct = mean(pct_correct)) %>%
                                       ungroup() %>%
                                       filter(session==2, isomorphic, group=="dihedral"))
```

# performance -> question relationship

```{r}
cc_model = glm(correspondence_correct ~ pct_correct, family="binomial", data=s2_joined_question_data %>% filter(! is.na(correspondence_correct)))
summary(cc_model)
```

# does education matter?
```{r}

time_dependent_education_model = glmer(action_correct ~ isomorphic * (education_high + session_c + I(session_c^2))  + group *  correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c | subject_id), family=binomial, data=main_data)
summary(time_dependent_education_model)
```

```{r}
time_dependent_education_interaction_model = glmer(action_correct ~ isomorphic * (session_c + I(session_c^2)) * education_high  + group *  correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c | subject_id), family=binomial, data=main_data)
summary(time_dependent_education_interaction_model)
```

# What if we consider the subset of the data where there appeared to be any learning at all?

```{r}
dihedral_data = main_data %>%
  select(-session_c, -trial_index_by_type_z) %>%
  filter(group == "dihedral") %>%
  mutate(session_c = scale(session, center=T, scale=F), # this is dumb
         trial_index_by_type_z = scale(trial_index_by_type, center=T, scale=T))
```


```{r}
dihedral_basic_non_time_dependent_model = glmer(action_correct ~ isomorphic * correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2) + (1 + session_c | subject_id), family=binomial, data=dihedral_data)
summary(dihedral_basic_non_time_dependent_model)
```

Time dependent:
```{r}
dihedral_basic_time_dependent_model = glmer(action_correct ~ isomorphic * correct_action + session_c + I(session_c^2) + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 +  session_c | subject_id), family=binomial, data=dihedral_data)
summary(dihedral_basic_time_dependent_model)
```


```{r}
dihedral_time_dependent_interaction_model = glmer(action_correct ~ isomorphic * (session_c + I(session_c^2)) *  correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1  + session_c | subject_id), family=binomial, data=dihedral_data)
summary(dihedral_time_dependent_interaction_model)
```
```{r}
dihedral_action_model = glmer(action ~ isomorphic * (correct_action + session_c + I(session_c^2)) + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 +  session_c | subject_id), family=binomial, data=dihedral_data)
summary(dihedral_action_model)
```

```{r}
dihedral_rt_time_dependent_model = lmer(location_rts/1000~ isomorphic  + (session_c + I(session_c^2)) + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c | subject_id), data=dihedral_data)
summary(dihedral_rt_time_dependent_model)
```


```{r}
dihedral_rt_time_dependent_interaction_model = lmer(location_rts/1000~ isomorphic * (session_c + I(session_c^2)) + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c  | subject_id), data=dihedral_data)
summary(dihedral_rt_time_dependent_interaction_model)
```

```{r}
num_steps_per_trial_data = dihedral_data %>%
  group_by(subject_id, isomorphic, session_c, trial_type, trial_index_by_type_z) %>%
  summarize(num_steps_needed=n())
```

```{r}
dihedral_ns_time_dependent_model = lmer(num_steps_needed~ isomorphic + (session_c + I(session_c^2))  + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c | subject_id), data=num_steps_per_trial_data)
summary(dihedral_ns_time_dependent_model)
```

```{r}
dihedral_ns_time_dependent_interaction_model = lmer(num_steps_needed~ isomorphic * (session_c + I(session_c^2))  + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c | subject_id), data=num_steps_per_trial_data)
summary(dihedral_ns_time_dependent_interaction_model)
```

```{r}
dihedral_time_dependent_education_model = glmer(action_correct ~ isomorphic * (education_high + session_c + I(session_c^2))+  correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c  | subject_id), family=binomial, data=dihedral_data)
summary(dihedral_time_dependent_education_model)
```

```{r}
dihedral_time_dependent_education_interaction_model =  glmer(action_correct ~ isomorphic * education_high * ( session_c + I(session_c^2)) + correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 | subject_id), family=binomial, data=dihedral_data)
summary(dihedral_time_dependent_education_interaction_model)
```

```{r}
dihedral_time_dependent_correct_int_education_model = glmer(action_correct ~ isomorphic * (education_high * correct_action + session_c + I(session_c^2))+   trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 + session_c  | subject_id), family=binomial, data=dihedral_data)
summary(dihedral_time_dependent_correct_int_education_model)
```
# Other subset

```{r}
dicyclic_data = main_data %>%
  select(-session_c, -trial_index_by_type_z) %>%
  filter(group == "dicyclic") %>%
  mutate(session_c = scale(session, center=T, scale=F), # this is dumb
         trial_index_by_type_z = scale(trial_index_by_type, center=T, scale=T))
```


```{r}
dicyclic_basic_non_time_dependent_model = glmer(action_correct ~ isomorphic * correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2) + (1 + session_c | subject_id), family=binomial, data=dicyclic_data)
summary(dicyclic_basic_non_time_dependent_model)
```

Time dependent:
```{r}
dicyclic_basic_time_dependent_model = glmer(action_correct ~ isomorphic * correct_action + session_c + I(session_c^2) + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1 +  session_c | subject_id), family=binomial, data=dicyclic_data)
summary(dicyclic_basic_time_dependent_model)
```


```{r}
dicyclic_time_dependent_interaction_model = glmer(action_correct ~ isomorphic * (session_c + I(session_c^2)) *  correct_action + trial_type + trial_index_by_type_z + I(trial_index_by_type_z^2)  + (1  + session_c | subject_id), family=binomial, data=dicyclic_data)
summary(dicyclic_time_dependent_interaction_model)
```
# What's the pattern in these huge action biases?
```{r}
xtabs(~ correct_action + action + group, data=main_data, na.action=na.pass, exclude=NULL)
```

# question by question prediction

```{r}
q2q_data = question_data %>% 
  filter(session == 2) %>%
  select(subject_id, fractal_dihedral, isomorphic, question, response) %>%
  spread(question, response) %>%
  mutate(education_high = grepl("PhD|Master|Bachelor", education),
         correspondence_suspected = correspondence_suspect == "Yes")
```

```{r}
xtabs( ~ isomorphic + fractal_dihedral + education_high, data=q2q_data)
```
```{r}
summary(glm(correspondence_suspected ~ education_high, family=binomial, data=q2q_data))

```


